Characterizing Stellar Streams by ML

### 2023-08-31 src/tex/ms.tex
[showyourwork] overleaf sync

    We would like to thank the Academy.

@@

        \package{asdf} \citep{Greenfield+2015}, \package{astropy}
        \citep{Astropy2013, Astropy2018, Astropy2022}, \package{astroquery}
        \citep{Astroquery2019}, \package{Matplotlib} \citep{Hunter2007},
        \package{NumPy} \citep{Harris+2020}, \package{Pytorch}
        \citep{Pytorch2019}, \package{SciPy} \citep{Scipy2020},
        \package{ShowYourWork} \citep{}

>>>>

    NS acknowledges support from the Natural Sciences and Engineering Research
    Council of Canada (NSERC) - Canadian Graduate Scholarships Doctorate Program
    [funding reference number 547219 - 2020].  NS received partial support from
    NSERC (funding reference number RGPIN-2020-04712) and from an Ontario Early
    Researcher Award (ER16-12-061; PI Bovy). NS would also like thank Prof. Webb
    for providing computational resources and travel funding.

    \JN{TODO}

@@

        \package{asdf} \citep{Greenfield+2015},%
        \package{astropy} \citep{Astropy2013, Astropy2018, Astropy2022},%
        \package{astroquery} \citep{Astroquery2019},%
        \package{Matplotlib} \citep{Hunter2007},%
        \package{NumPy} \citep{Harris+2020},%
        \package{Pytorch} \citep{Pytorch2019},%
        \package{SciPy} \citep{Scipy2020},%
        \package{ShowYourWork} \citep{Luger2021}%
